### 2015-05-13 Draft/background.tex
Minor gramatical edits

{\small $\bullet$} \textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}:
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, reduction in the number of lexical tokens greatly improves the accuracy of core NLP techniques. 
In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
%These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.

%\item \textit{Period Handling}: Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
%Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
%The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.
\vspace*{-1.5ex}
\begin{itemize}

\item \textit{Named Entity Handling}: Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
Further resolution of such phrases using grammatical syntax may not bring forth any semantic value.
Also these phrases contribute to length of a sentence that in turn negatively affects the accuracy of core NLP techniques.
This heuristic annotates the phrase representing the name of the entities as a single lexical token.

>>>>

{\small $\bullet$} \textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}:
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, reduction in the number of lexical tokens greatly improves the accuracy of core NLP techniques. 
In particular, following heuristics have been used in our previous work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:
%These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.

%\item \textit{Period Handling}: Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
%Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
%The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.

\begin{itemize}

\item \textit{Named Entity Handling}: Sometimes a sequence of words correspond to the name of entities that have a specific meaning collectively.
For instance, consider the phrases \textit{``Amazon S3'', ``Amazon simple storage service''}, which are the names of the service.
Further resolution of such phrases using grammatical syntax is redundant for inference needs.
This heuristic annotates the phrase representing the name of an entity as a single lexical token,
to improve accuracy of core NLP techniques.

### 2015-05-13 Draft/related.tex
Minor gramatical edits

Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664,wasylkowski2011mining} from source code and binaries. 
Among mining based approaches Gable and Su~\cite{gabel2008javert} proposed to learn  
\textit{micropatterns} of temporal properties from runtime traces and then combining them into larger specifications depicted as finite state automata.
In contrast, \tool\ infers specifications from the natural language text in API documents,
thus complementing existing approaches when the source code or binaries of the API library is not available.

>>>>

Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664,wasylkowski2011mining} from source code and binaries. 
Among mining based approaches Gable and Su~\cite{gabel2008javert} proposed to learn  
\textit{micro-patterns} of temporal properties from runtime traces and then combining them into larger specifications depicted as finite state automata.
In contrast, \tool\ infers specifications from the natural language text in API documents,
thus complementing existing approaches when the source code or binaries of the API library is not available.
